---
title: "SysBioSig Theme"
author: "Karol Nienałtowski"
output:
  html_document:
    df_print: paged
email: k.nienaltowski@sysbiosig.org
vignette: |
  %\VignetteIndexEntry{Vignette Title} %\VignetteEngine{knitr::rmarkdown} %\VignetteEncoding{UTF-8} \usepackage[utf8]{inputenc}
---


### Installation

ITRC package can be installed usign `devtools` package as following

```{r echo=TRUE, eval=FALSE}
install.packages("devtools") # if devtools package is not installed
require(devtools)
devtools::install_github("stork119/SysBioSigTheme", auth_token = [AUTHORISATION_TOKEN])
```
`[AUTHORISATION_TOKEN]` can be obtained  on request after sending an email on address <k.nienaltowski@sysbiosig.org>.

To attatch `SysBioSigTheme` functions use:
```{r echo=TRUE, eval=TRUE, message=FALSE}
library(SysBioSigTheme)
```

### Normalise data 
To read data tables generated by Cell Profiller and IPIQA it is necessary to use normalisation function 
```{r echo=TRUE, eval=FALSE}
data <- normalize_data(read.table([PATH_TO_FILE],
                                   header=TRUE, sep=","))$data
```


### Scatter plots
In order to plot novel scatter plots use functions `ScatterBoxplotGGplot`:

```{r echo=TRUE, eval=TRUE, fig.width=8, fig.height=4}

ScatterBoxplotGGplot(data = SysBioSigTheme::data.jarek,
                     x_ = "stimulation.1.1",
                     y_ = "Intensity_MeanIntensity_Alexa") +
  coord_cartesian(ylim = c(0,50))
```

or `ScatterViolinGGplot`:

```{r echo=TRUE, eval=TRUE, fig.width=8, fig.height=4}
ScatterViolinGGplot(data = SysBioSigTheme::data.jarek,
                     x_ = "stimulation.1.1",
                     y_ = "Intensity_MeanIntensity_Alexa") +
  coord_cartesian(ylim = c(0,50))
```
