---
title: "SysBioSig Theme"
author: "Karol Nienałtowski"
output:
  html_document:
    df_print: paged
  pdf_document: default
email: k.nienaltowski@sysbiosig.org
vignette: |
  %\VignetteIndexEntry{Vignette Title} %\VignetteEngine{knitr::rmarkdown} %\VignetteEncoding{UTF-8} \usepackage[utf8]{inputenc}
---


### Installation

ITRC package can be installed usign `devtools` package as following

```{r echo=TRUE, eval=FALSE}
install.packages("devtools") # if devtools package is not installed
require(devtools)
devtools::install_github("stork119/SysBioSigTheme", auth_token = [AUTHORISATION_TOKEN])
```
`[AUTHORISATION_TOKEN]` can be obtained  on request after sending an email on address <k.nienaltowski@sysbiosig.org>.

To attatch `SysBioSigTheme` functions use:
```{r echo=TRUE, eval=TRUE, message=FALSE}
library(SysBioSigTheme)
```

### Normalise data 
To read data tables generated by Cell Profiller and IPIQA it is necessary to use normalisation function 
```{r echo=TRUE, eval=FALSE}
data <- normalize_data(read.table([PATH_TO_FILE],
                                   header=TRUE, sep=","))$data
```

### Themes
Instead of `theme_jetka()` you can use new theme function `theme_sysbiosig()`

### Scatter plots
In order to plot novel scatter plots use functions `ScatterBoxplotGGplot`:

```{r echo=TRUE, eval=TRUE, fig.width=8, fig.height=4}

ScatterBoxplotGGplot(data = SysBioSigTheme::data.jarek,
                     x_ = "stimulation.1.1",
                     y_ = "Intensity_MeanIntensity_Alexa") +
  coord_cartesian(ylim = c(0,50))
```

or `ScatterViolinGGplot`:

```{r echo=TRUE, eval=TRUE, fig.width=8, fig.height=4}
ScatterViolinGGplot(data = SysBioSigTheme::data.jarek,
                     x_ = "stimulation.1.1",
                     y_ = "Intensity_MeanIntensity_Alexa") +
  coord_cartesian(ylim = c(0,50))
```


### Additional Parameters
You can change limits of the densities colors  using parameter `colors.limits`:

```{r echo=TRUE, eval=TRUE, fig.width=8, fig.height=4}

ScatterBoxplotGGplot(data = SysBioSigTheme::data.jarek,
                     x_ = "stimulation.1.1",
                     y_ = "Intensity_MeanIntensity_Alexa",
                     colors.limits = c(0, 0.025)) +
  coord_cartesian(ylim = c(0,50))
```


You can rescale colors pallete densities colors  using parameter `density.rescale.fun`.
Parameter `density.rescale.fun` defines a function used for rescaling signals in plots. There are three built-in functions, that can be chosen: (1) 'numeric', (2) logarithmic - with base defined in density.rescale.fun.args - default: e = exp(1). Function must be defined as a lambda construct function(x, ...){...}.
If you want to use logarithimic scale of densities colors set parameter `density.rescale.fun = "log"`. 


```{r echo=TRUE, eval=TRUE, fig.width=8, fig.height=4}

ScatterBoxplotGGplot(data = SysBioSigTheme::data.jarek,
                     x_ = "stimulation.1.1",
                     y_ = "Intensity_MeanIntensity_Alexa",
                     density.rescale.fun = "log") +
  coord_cartesian(ylim = c(0,50))
```


You can also use your own function. For example `density.rescale.fun = function(x){5*log(x, base = 10)}`. 

```{r echo=TRUE, eval=TRUE, fig.width=8, fig.height=4}

ScatterBoxplotGGplot(data = SysBioSigTheme::data.jarek,
                     x_ = "stimulation.1.1",
                     y_ = "Intensity_MeanIntensity_Alexa",
                     density.rescale.fun = function(x){5*log(x, base = 10)}) +
  coord_cartesian(ylim = c(0,50))
```


You can modify themes by adding special thee parameters. All possible parameters of theme function you can find in `theme` description `?theme`. For instance you can manipulate position of the legend using `legend.position`. You can choose `("none", "left", "right", "bottom", "top", or two-element numeric vector)`. For instance legend is removed, when `legend.position = "none"`.

```{r echo=TRUE, eval=TRUE, fig.width=8, fig.height=4}

ScatterBoxplotGGplot(data = SysBioSigTheme::data.jarek,
                     x_ = "stimulation.1.1",
                     y_ = "Intensity_MeanIntensity_Alexa",
                     legend.position = "none") +
  coord_cartesian(ylim = c(0,50))
```

